---
title: "Visualization"
suntitle: "Part I"
output: github_document
author: Shunyi Zhang
editor_options: 
  chunk_output_type: console
---

```{r setup}
library(tidyverse)
library(ggridges)
```

## Load the Weather Data

```{r tidy data}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"),
    date_min = "2017-01-01",
    date_max = "2017-12-31"
  ) %>% 
  mutate(
    name = recode(
      id,
      USW00094728 = "CentralPark_NY",
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"
    ),
    tmin = tmin / 10,
    tmax = tmax / 10
  ) %>% 
  select(name, id, everything())

head(weather_df)
```


## Basic Scatterplots

### Create forst scatterplot.

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point()
```

### Another approach. (fit overall syntax)

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point()
```

### Save and edit a plot object. (least frequently)

```{r}
weather_plot = 
  weather_df %>% 
  ggplot(aes(x = tmin, y = tmax))

weather_plot + geom_point()
```


## Advanced Scatterplots

### Make basics fancy

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + ##define another aesthetic mapping "color"
  geom_point() + 
  geom_smooth(se = FALSE) ##new geometry: geom_smooth, se = standard error, generally turnned off
##`color = name` in ggplot() generate separate lines for each of 3 name factor. 
```

### About the 'aes' replacement

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name)) +
  geom_smooth() 
##`color = name` inn geom_point() generate one single blue line running through all
```

### Facet

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point() + 
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name) ##a multi-planel plot
```
`. ~name`, `.`means don't create rows, `name` defines columns. `~` called tilde. 

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point() + 
  geom_smooth(se = FALSE) +
  facet_grid(name ~ .)
```
the reverse for the previous one.

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = .2) +      ##alpha level for transparency
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name)
```

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, alpha = tmin, color = name)) + 
  ##alpha level be related to the precipitation variable
  geom_point() +      
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name)
```

### Combine elements

```{r}
weather_df %>% 
  ggplot(aes(x = date, y = tmax, color = name)) + 
  geom_point(aes(size = prcp), alpha = 0.5) + 
  geom_smooth(se = FALSE) + 
  facet_grid(. ~ name)
```


### Small Notes

```{r many geoms exist, have whatever you need}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_smooth(se = FALSE)
```

```{r neat geom}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_hex() +
  geom_density2d()
```


## Univariate plots

### Histograms

```{r}
weather_df %>% 
  ggplot(aes(x = tmin)) + 
  geom_histogram()
```

```{r add color to histogram}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) + 
  geom_histogram() + ##option: (position = "dodge")
  facet_grid(. ~ name) ##don't need color or fill b/c separate plots
```

```{r `geom_density(alpha, adjust)`} 
weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) + 
  geom_density(alpha = .3)
```

### Boxplot 

```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmin)) +
  geom_boxplot()
```

### Trendy plot

```{r}
weather_df %>% 
  ggplot(aes(x =name, y = tmin, fill = name)) +
  geom_violin(alpha = .5) + ##cross between boxplot and density plot 
  stat_summary(fun = "median")
```

### Ridge plot -- most popular in 2017

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = name)) +
  geom_density_ridges()
```


## Same and Embed

### Save

```{r}
weather_plot =
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .5)

ggsave("./results/weather_plot.pdf", weather_plot, width = 8, height = 5)
```

### Embeding

```{r,fig.width=6, fig.height=3}
weather_plot
```

```{r,fig.width=12, fig.height=6}
weather_plot
```
